\section{Team Code of Conduct}

To support a productive and respectful working environment, our team agrees to follow the principles outlined below. These guidelines define how we interact, collaborate, and manage our responsibilities throughout the project.

\subsection{Communication Standards}
\begin{itemize}
    \item Communicate clearly, respectfully, and professionally with all team members.
    \item Ensure that everyone has the chance to share ideas, raise concerns, and give feedback.
    \item Reply to messages and emails from teammates within a 24-hour period.
\end{itemize}

\subsection{Teamwork and Collaboration}
\begin{itemize}
    \item Contribute fairly to group work and support one another in completing tasks.
    \item Take responsibility for individual duties while holding each other accountable as a team.
    \item Show flexibility and understanding toward the different commitments and circumstances of team members.
\end{itemize}

\subsection{Compliance with Rules and Policies}
\begin{itemize}
    \item Follow all project-related rules and expectations outlined in this document and elsewhere.
    \item Act in accordance with University policies and academic regulations at all times.
\end{itemize}

\subsection{Attendance, Availability \& Exceptional Circumstances}
All team members are expected to attend scheduled lectures, labs, sprint reviews, and group presentations. The affected team member must inform the group as early as possible (at least 12 hours in advance) via WhatsApp.

\subsection{Managing Non-Compliance}
If a team member is unable to attend a meeting or lab, they can receive a summary. Continued absence without prior communication may be reported to the module tutor. Ongoing failure to complete assigned tasks will be discussed as a group.
