\section{User Stories}

\begin{itemize}
    \item \textbf{US1 – Create profile:} As a student, I want to create a profile with my course, year and modules so that other students can understand what I study.
    \item \textbf{US2 – Login to account:} As a student, I want to log in to my account so that my profile and activity are kept secure.
    \item \textbf{US3 – Search by module:} As a student, I want to search for study buddies by module so that I can find someone studying the same subject.
    \item \textbf{US4 – View user profiles:} As a student, I want to view another student’s profile so that I can decide if they are a good match for studying together.
    \item \textbf{US5 – Send study request:} As a student, I want to send a study request to another student so that I can organise a study session.
    \item \textbf{US6 – Accept or decline requests:} As a student, I want to accept or decline study requests so that I can control who I study with.
    \item \textbf{US7 – Dashboard:} As a student, I want to see upcoming study sessions and pending requests in one place so that I can arrange my study plans easily.
    \item \textbf{US8 – Filter by availability:} As a student, I want to filter study buddies by availability so that I can find someone who is free at similar times.
    \item \textbf{US9 – Ratings and feedback:} As a student, I want to leave feedback after a study session so that other students can feel more confident when choosing a study partner.
    \item \textbf{US10 – Report or block a user:} As a student, I want to report or block a user so that I feel safe if someone behaves inappropriately.
\end{itemize}
